---
output: github_document
---


# Macroeconomics (2017Q4) @ GSE, KobeU

Homework Assignments and optional exercises for Macroeconomics Q4 @ GSEcon, Kobe University

```{r, include=FALSE}
library(tidyverse)
data <- readr::read_csv("../assignments.csv")
org <- "https://github.com/rokko-ma17q4/"
```

## Assignments

Assignments with prefix "hw" are mandatory and those with "ex" are optional (you'll get bonus points).

```{r, echo=FALSE, warning=FALSE}
pdata <- data %>% 
  mutate(ID = paste0("[", ID, "](", org, ID ,")")) %>%
  mutate(`Invitation Link` = paste0("[Get Invitation]", "(", Link, ")")) %>% 
  select(ID, `Suggested Deadline`, Description, `Invitation Link`, Solution) %>%
  arrange(lubridate::mdy_hm(`Suggested Deadline`))
knitr::kable(pdata)
```

## Submission record

Don't you forget to open a Pull Request? See this [list of PRs](https://github.com/issues?utf8=%E2%9C%93&q=is%3Apr+user%3Arokko-ma17q4). 

## Additional Information

If you plan to use at a computer at the computer lab, you might want to 
know several techniques to install applications on Mac. See [hw-portal/Wiki](https://github.com/rokko-ma17q4/hw-portal/wiki)


Here is a series of notes concerning R, R Markdown and related stuff.

* [Quick Tutorial for R Markdown](https://cdn.rawgit.com/kenjisato/tips/2e4d7a9d/rmarkdown-basic/basic.html)


